\documentclass[acmtog, review, anonymous]{acmart}

\usepackage{booktabs} % For formal tables

% TOG prefers author-name bib system with square brackets
\citestyle{acmauthoryear}
\setcitestyle{square}


\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmJournal{TOG}
% \acmVolume{9}
% \acmNumber{4}
% \acmArticle{39}
% \acmYear{2010}
% \acmMonth{3}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
% \setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
% \acmDOI{0000001.0000001_2}

% Paper history
% \received{February 2007}
% \received{March 2009}
% \received[final version]{June 2009}
% \received[accepted]{July 2009}

% Document starts
\begin{document}
% Title portion
\title{OptCuts: Joint Optimization for Seam Placement and Parameterization of 3D Surfaces} 

\author{Minchen Li}
% \orcid{1234-5678-9012-3456}
% \affiliation{%
%   \institution{College of William and Mary}
%   \streetaddress{104 Jamestown Rd}
%   \city{Williamsburg}
%   \state{VA}
%   \postcode{23185}
%   \country{USA}}
\email{minchernl@gmail.com}
% \author{Valerie B\'eranger}
% \affiliation{%
%   \institution{Inria Paris-Rocquencourt}
%   \city{Rocquencourt}
%   \country{France}
% }
% \email{beranger@inria.fr}
% \author{Aparna Patel} 
% \affiliation{%
%  \institution{Rajiv Gandhi University}
%  \streetaddress{Rono-Hills}
%  \city{Doimukh} 
%  \state{Arunachal Pradesh}
%  \country{India}}
% \email{aprna_patel@rguhs.ac.in}
% \author{Huifen Chan}
% \affiliation{%
%   \institution{Tsinghua University}
%   \streetaddress{30 Shuangqing Rd}
%   \city{Haidian Qu} 
%   \state{Beijing Shi}
%   \country{China}
% }
% \email{chan0345@tsinghua.edu.cn}
% \author{Ting Yan}
% \affiliation{%
%   \institution{Eaton Innovation Center}
%   \city{Prague}
%   \country{Czech Republic}}
% \email{yanting02@gmail.com}
% \author{Tian He}
% \affiliation{%
%   \institution{University of Virginia}
%   \department{School of Engineering}
%   \city{Charlottesville}
%   \state{VA}
%   \postcode{22903}
%   \country{USA}
% }
% \affiliation{%
%   \institution{University of Minnesota}
%   \country{USA}}
% \email{tinghe@uva.edu}
% \author{Chengdu Huang}
% \author{John A. Stankovic}
% \author{Tarek F. Abdelzaher}
% \affiliation{%
%   \institution{University of Virginia}
%   \department{School of Engineering}
%   \city{Charlottesville}
%   \state{VA}
%   \postcode{22903}
%   \country{USA}
% }

\renewcommand\shortauthors{Li, M. et al}

\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{green}{rgb}{0, 0.6, 0}
\definecolor{orange}{rgb}{1, 0.5, 0}
\definecolor{mahogany}{rgb}{0.75, 0.25, 0.0}
\definecolor{purple}{rgb}{0.6, 0, 0.6}
\definecolor{darkgreen}{rgb}{0, 0.3, 0}
\definecolor{orange}{rgb}{1, 0.5, 0.}
\newcommand{\minchen}[1]{\textcolor{blue}{\textbf{Minchen: #1}}}

\begin{abstract}
% context and need
Parameterizing 3D surfaces to the 2D plane is a fundamental problem with many applications in texture mapping, remeshing, and detail transfer, etc.
For most surfaces, one has to introduce discontinuities (seams) and distortion while producing a map. Existing techniques typically decide between the two independently: first placing seams and then minimizing distortion, and thus produce sub-optimal results.
% task and object
We propose {\em OptCuts}, a joint discrete-continuous optimization framework that progressively place seams in between distortion minimizations, where the objective is a linear combination of a distortion energy and seam length. The stationary w.r.t. both UV topology and coordinates are guaranteed to be reached within a bounded number of iterations per balancing factor, input model, and initial embedding.
Starting with an initial embedding, OptCuts alternates between topology steps and descent steps to search for an optimal UV map. In topology steps, it first finds a search direction in the UV topology space that locally decrease the objective the most; and then in the following descent step, it decides the topology search step-size by a newly derived forward-tracking line search scheme alternated with distortion minimization.
Since in application scenarios, an upper bound for distortion is more intuitive than picking a balancing factor, we also provide a constrained optimization formulation that seeks stationary w.r.t. both primal (UV coordinates and topology) and dual (balancing factor) variables subject to user specified distortion upper bounds.
% conclusion
We demonstrate in the experiment that OptCuts automatically produces high quality UV maps without any user assistance, and it can generate seams targeting on different types of distortion measurement or respecting user preferences on regional seam placement.
We show that our discrete-continuous optimization framework also has the potential to jointly handle global bijectivity and seamlessness.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
	<concept>
		<concept_id>10010147.10010371.10010396.10010398</concept_id>
		<concept_desc>Computing methodologies~Mesh geometry models</concept_desc>
		<concept_significance>500</concept_significance>
	</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Mesh geometry models}

%
% End generated code
%


\keywords{geometry processing, mesh parameterization, seam placement, numerical optimization, ...}



\maketitle

\input{introduction}

\input{relatedWorks}

\input{alternatingFramework}

\input{descentSteps}

\input{topologySteps}

\input{autoWeighting}

\input{results}

\input{conclusions}

\bibliographystyle{ACM-Reference-Format}
\bibliography{OptCuts} 

\end{document}
